\documentclass{muratcan_cv}

\setname{Batuhan}{UZUN}
\setaddress{Istanbul/Turkey}
\setmobile{+90 *** *** ****}
\setmail{batuhanuzun\_@outlook.com}
\setposition{Work Student} %ignored for now
\setlinkedinaccount{https://www.linkedin.com/in/uzunb/} %you can play with color of the template (red is also nice..)
\setgithubaccount{https://github.com/uzunb} %you can play with color of the template (red is also nice..)
    \setthemecolor{Turquoise} %you can play with color of the template (red is also nice..) FARKLI RENKLER DENE.
    

\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
% Summary
\addblocktext{Summary}{%
I am passionate about robotics, vision, perception and intelligence systems. I value good software engineering practices, collaboration and working with people who I can learn from. Some of features are my insistency on projects that i work on, ability of learning anything around me, durability against hard situations.
}
%
%Education
\section{Education} 
    \datedexperience{Karadeniz Technical University}{2017-present} 
    \explanation{Bachelor of Engineering in Computer Science - GPA 3.02} 
    \datedexperience{Maltepe Orhangazi Anatolian Imam Hatip High School}{2012-2017} 
    %\explanation{M.S in Informatics} 
    %\explanationdetail{\coloredbullet\ %
    % \lipsum[1][3-4]\par %replace this part with actual text
    % }
%
% Experience
\section{Experience}
    %
    \datedexperience{Hangar Tech Team}{Apr 2019 - present} 
    \explanation{Team Leader} 
    \explanationdetail{\coloredbullet\ %
        An autonomous unmanned aircraft vehicle (UAV) has been developed for TeknoFest 2020.
     }
    %
    %
    \datedexperience{HAVELSAN}{Sep 2020 - Oct 2020} 
    \explanation{Intern} 
    \explanationdetail{\coloredbullet\ %
        Augmented reality tank simulation has been developed with Unity.
     }
    %
    %
    \datedexperience{TUBITAK}{March 2020 - Sep 2020} 
    \explanation{Python Developer - Part time} 
    \explanationdetail{\coloredbullet\ %
        As a scholarship student, a Turkish Python editor was developed with the PyQt5 Framework.
     }
    %
    \datedexperience{Anıl Electronic}{Jun. 2019 - Sep. 2019} 
    \explanation{Assembler} 
    \explanationdetail{\coloredbullet\ %
        Fix PCB cards.
     }
    
%


% Projects
\section{Projects}
   %
    \datedexperience{Artificial Neural Network}{} 
    \explanation{Multilayer Multicategory Learning Rules} 
    \explanationdetail{\coloredbullet\ %
        Visual C++ used in the GUI.  The project continues. Single layer single neuron Perceptron and Delta learning rules was implemented with C/C++.
     }
     %
    %
    \datedexperience{Image Processing on Bitmap Pictures}{} 
    \explanation{Image Segmentation \& Classification, Line \& Circle Detection} 
    \explanationdetail{\coloredbullet\ %
        Visual C++ used in the GUI. Automatic threshold detection algorithms, feature extraction, object recognition, Canny edge detection, Hough Transform Algorithms are implemented with C.
     }
     %
       %
    \datedexperience{Target detection with OpenCV}{} 
    \explanation{ Real-time red color target detection} 
    \explanationdetail{\coloredbullet\ %
        Implemented in Raspberry Pi 4 with C++ OpenCV Library.
     }
     %
     %
    \datedexperience{Bank Management System}{} 
    \explanation{ Allows you to manage your bank accounts with a single application. } 
    \explanationdetail{\coloredbullet\ %
        Implemented with Python(OOP), PyQt5 Framework in GUI, database model in MySQL.
     }
     %
     %
    \datedexperience{Python Editor for children}{} 
    \explanation{ A Python editor that can make easy to learn Python programming language for children. } 
    \explanationdetail{\coloredbullet\ %
        Implemented with Python, PyQt5 Framework in GUI, database model in MySQL.
     }
     %
     %
    \datedexperience{Word Hunter}{} 
    \explanation{ Developing a new algorithm based on Mastermind game. } 
    \explanationdetail{\coloredbullet\ %
        It is a desktop application that uses the Qt Framework. The application finds words using the improved Mastermind game algorithm.
     }
     %
     %
    \datedexperience{Encrypted Mail System}{} 
    \explanation{ Mail system that sends your mail text in encrypted form.} 
    \explanationdetail{\coloredbullet\ %
        Implemented with C++(OOP) and RSA encryption algorithm. 
     }
     %
      %
    \datedexperience{Library System}{} 
    \explanation{ Library console application which can able library operations (CRUD).} 
    \explanationdetail{\coloredbullet\ %
        Implemented with C++(OOP).
     }
     %
    
     
%

% Skills
\section{Skills}
    %
    \newcommand{\skillone}{\createskill{Programming Languages}{\textbf{\emph{Experienced:}} \ \ C \cpshalf C++ \cpshalf Python  \ \ \textbf{\emph{Familiar:}} \ \  C\#  \cpshalf Bash \cpshalf Java}}
    %
    \newcommand{\skilltwo}{\createskill{Software Development}{ Linux \cpshalf GIT \cpshalf SQL \cpshalf Software Design Patterns \cpshalf Embedded Systems \cpshalf CLI}}
    %
    \newcommand{\skillthree}{\createskill{Frameworks \ \& \ Libraries}{Qt5 \cpshalf PyQt5 \cpshalf OpenCV \cpshalf Matplotplib \cpshalf Numpy \cpshalf Pandas \cpshalf Scikit-learn}}
    %
    \newcommand{\skillfour}{\createskill{Languages}{\textbf{\emph{Native:}} \ \  Turkish \ \ \textbf{\emph{Intermediate:}} \ \ English \ \ }}
    %
    \createskills{\skillone, \skilltwo, \skillthree, \skillfour}
%

% Cources & CERTIFICATES
\section{Cources \& Certificates}
    %
    \newcommand{\courceone}{%
    Udemy | Python Course From Basic to Advanced
    }
    %
    \newcommand{\courcetwo}{%
    Udemy | GPU (CUDA) Programming
    }
    %
    \newcommand{\courcethree}{%
    Udemy | Machine Learning with Python
    }
    %
    \newcommand{\listofcource}{\courceone, \courcetwo, \courcethree}
    %
    \createbullets{\listofcource}
%

% Experience
\section{Extra}
    %
    \newcommand{\extraone}{%
    5th TÜBİTAK International Unmanned Aerial Vehicle Competition - İYC-Kokpit Team - Team leader
    }
    %
    \newcommand{\extratwo}{%
    I am the team leader of  the projects those are held in Hangar Technology R\&D workshop.
    }
    \newcommand{\extrathree}{%
    I am currently a member of student clubs those are IEEE and SAVSISTEK(Defence industry club). I usually have duties such as being Python instructor and event organizer.
    }
    %
    \newcommand{\extrafour}{%
    I give importance to read books in order to improve myself. Especially historical and world classics.
    }
    %
    %
    \newcommand{\extrafive}{%
    I frequently play basketball with my close friends.
    }
    %
    \newcommand{\listofextras}{\extraone, \extratwo, \extrathree, \extrafour, \extrafive}
    %
    \createbullets{\listofextras}
%

\end{document}
